### 2023-03-14 README.Rmd
Deploying to gh-pages from @ gavinsimpson/gratia@88e289c9186924b234f185dfb8820d512726c988 🚀

```{r install-r-universe, eval = FALSE}
# Enable repository from gavinsimpson
options(repos = c(
  gavinsimpson = "https://gavinsimpson.r-universe.dev",
  CRAN = "https://cloud.r-project.org"))

# Download and install gratia in R
install.packages("gratia")
```

>>>>

```{r install-r-universe, eval = FALSE}
# Install gratia in R
install.packages("gratia", repos = c("https://gavinsimpson.r-universe.dev",
  "https://cloud.r-project.org"))
```
